Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-09-02 article/draft.tex
change youtube panels results after running the scraper without connecting to a US server

To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information. 
We collected the information panels, when present, under each video by connecting to a US server and scraping the content of the web page. 
Five types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19, U.S. elections and vaccination information, as shown in figure \ref{youtube_panel_screenshots}.

\begin{figure}[h]
	\centering
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
		\includegraphics[scale=0.29]{./img/youtube_panels/yt_2.png} 
		\includegraphics[scale=0.294]{./img/youtube_panels/yt_3.png}
		\includegraphics[scale=0.305]{./img/youtube_panels/yt_4.png} 
		\includegraphics[scale=0.193]{./img/youtube_panels/yt_5.png} 
	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19}, \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections} and \href{https://www.youtube.com/watch?v=OuQYMjpCwfU}{vaccination information}. The videos were accessed on July 21, 2021 from a US server.}
	\label{youtube_panel_screenshots}
\end{figure}

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multicolumn{6}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
\makecell{Without \\ any \\ panel} & 
\makecell{With a \\ `COVID-19' \\ panel} & 
\makecell{With a \\ `COVID-19 \\ vaccine' panel} &
\makecell{With a \\ `climate change' \\ panel} &
\makecell{With a \\ `U.S. elections' \\ panel} &
\makecell{With a \\ `vaccination \\ information' panel}  
\\ \hline
\makecell{74 \\ (44 \%)} &
\makecell{71 \\ (42 \%)} &
\makecell{19 \\ (11 \%)} &
\makecell{4 \\ (2 \%)} &
\makecell{1 \\ (0.5 \%)} &
\makecell{1 \\ (0.5 \%)}
\\ \hline
\end{tabular}
\caption{Summary of the number of YouTube videos wich contain a certain information panel, among the set of videos marked as false or inaccurate by Science Feedback.}
\label{youtube_panel_proportions}
\end{table}

@@

Almost half (44 \%) of the videos containing misinformation were shown without any information panel (Table \ref{youtube_panel_proportions}).
For the rest of videos, the most frequent information panels concerned COVID-19 (42 \%) and COVID-19 vaccine (11 \%).
It is possible that YouTube is currently focusing its efforts on the current `hot' controversial topics with a potentially wide public impact, leaving room for misinformation related to other topics to spread, but more research is needed to formally compare misinformation videos about COVID-19 and about other subjects.

>>>>

To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information. 
We collected the information panels, when present, under each video by scraping the content of the web page. 
Three types of information panels were found regarding COVID-19, COVID-19 Vaccine, and climate change, as shown in figure \ref{youtube_panel_screenshots}.

\begin{figure}[h]
	\centering
		\includegraphics[scale=0.2]{./img/youtube_panels/youtube_panel_covid.png} 
		\includegraphics[scale=0.2]{./img/youtube_panels/youtube_panel_covid_vaccine.png} 
		\includegraphics[scale=0.2]{./img/youtube_panels/youtube_panel_climate.png}
	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=O1cFVdC2rZQ}{COVID-19}, \href{https://www.youtube.com/watch?v=v0-6JTr2Ifo}{COVID-19 Vaccine} and \href{https://www.youtube.com/watch?v=4U8kgiiVj5Q}{climate change}. The videos were accessed on September 2, 2021.}
	\label{youtube_panel_screenshots}
\end{figure}

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
\makecell{Without \\ any panel} & 
\makecell{With a \\ `COVID-19' \\ panel} & 
\makecell{With a \\ `COVID-19 vaccine' \\ panel} &
\makecell{With a \\ `climate change' \\ panel}
\\ \hline
\makecell{78 \\ (46 \%)} &
\makecell{71 \\ (42 \%)} &
\makecell{15 \\ (9 \%)} &
\makecell{6 \\ (3 \%)}
\\ \hline
\end{tabular}
\caption{Summary of the number of YouTube videos wich contain a certain information panel, among the set of videos marked as false or inaccurate by Science Feedback.}
\label{youtube_panel_proportions}
\end{table}

@@

Almost half (46 \%) of the videos containing misinformation were shown without any information panel (Table \ref{youtube_panel_proportions}).
For the rest of videos, the most frequent information panel concerned COVID-19 (42 \%), followed by COVID-19 vaccine (9 \%).
It is possible that YouTube is currently focusing its efforts on the current `hot' controversial topics with a potentially wide public impact, leaving room for misinformation related to other topics to spread, but more research is needed to formally compare misinformation videos about COVID-19 and about other subjects.
